%!TEX program = xelatex

\documentclass[11pt,fullpage]{article}
\usepackage[dvipsnames]{xcolor}

\usepackage[colorlinks,allcolors=BrickRed]{hyperref}
\usepackage{geometry}
\usepackage{listliketab}
\usepackage{array}
\usepackage{longtable}
\usepackage{etoolbox}
\usepackage{natbib}
\usepackage{bibentry}
\usepackage{colortbl}

\nobibliography*
%\bibliographystyle{apa}

% Palatino font
% \usepackage[T1]{fontenc}
% \usepackage[sc,osf]{mathpazo}

% \usepackage[math]{iwona}
% \usepackage[T1]{fontenc}


\usepackage[sfdefault]{FiraSans} %% option 'sfdefault' activates Fira Sans as the default text font
\usepackage[T1]{fontenc}
\renewcommand*\oldstylenums[1]{{\firaoldstyle #1}}



% \usepackage[math]{kurier}
% \usepackage[T1]{fontenc}

% \usepackage[nf]{coelacanth}
% \usepackage[T1]{fontenc}
% %% The font package uses mweights.sty which has som issues with the
% %% \normalfont command. The following two lines fixes this issue.
% \let\oldnormalfont\normalfont
% \def\normalfont{\oldnormalfont\mdseries}



\def\name{Philip S. Chodrow}

\reversemarginpar

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.0in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\mdseries\Large}
% \subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}


% \def\Long{0}
% \def\Long{0}
\newtoggle{Long}
\toggletrue{Long}
% \togglefalse{Long}

\newcommand{\hide}[1]{
   % \ifnum\Long=1
 
   % #1 \vspace{\baselineskip}
   % \fi
 
   % \ifnum\Long=0
   % % \vspace{2\baselineskip} \hspace{2cm}
   % \fi
   \iftoggle{Long}{
   #1
   }{}
}


\begin{document}
\bibliographystyle{apalike}

% Print name centered and bold:
\centerline{\Large \bf \name}

% \vspace{0.25in}

% \begin{minipage}{0.50\linewidth}
%   Massachusetts Institute of Technology \\
%   \iftoggle{Long}{
% 	  Operations Research Center \\
% 	  % \href{https://lids.mit.edu/}{Laboratory for Information and Decision Systems} \\ 
%   }{}
%   77 Massachusetts Avenue \\
%   Cambridge, MA 02139
% \end{minipage}
% \begin{minipage}{0.50\linewidth}
%   \begin{tabular}{ll}
%     % Phone: & (212) 998-8578 \\
%     Website: & \href{https://philchodrow.com}{philchodrow.com} \\
%     Email: & \href{mailto:pchodrow@mit.edu}{pchodrow@mit.edu} \\
%     GitHub: & \href{https://github.com/PhilChodrow}{PhilChodrow} \\
%     Twitter: & \href{https://twitter.com/PhilChodrow}{PhilChodrow} \\
%     % Homepage: & \href{http://www.christinabergey.com/}{www.christinabergey.com} \\
%   \end{tabular}
% \end{minipage}

\begin{center}
Massachusetts Institute of Technology \\ 
77 Massachusetts Avenue, Cambridge, MA 02139

\url{pchodrow@mit.edu} $\diamond$  \href{https://www.philchodrow.com}{\texttt{www.philchodrow.com}} $\diamond$ he/him/his
\end{center}


% \section*{Summary}
% \vspace{3em}

% I am an applied mathematician developing models and methods for studying adaptive complex systems. 
% My methodological interests include stochastic processes, information theory, and spatial statistics. 
% My application areas include network inference; opinion dynamics; demographic segregation; and estimation problems in spatial growth processes. 


\section*{Education}
	\vspace{-10pt}
	\setlength{\extrarowheight}{5pt}
	\begin{longtable}{p{0.6in}|p{5.5in}}
		2015- & {\bf Ph.D. Candidate} in Operations Research, MIT. Expected graduation May, 2020. \\
		2008-12 & {\bf B.A. with High Honors} in  Mathematics and Philosophy, Swarthmore College. 
	\end{longtable}

\section*{Selected Papers}
	\vspace{-10pt}
	% \bibliographystyle{ieeetr} 
	\setlength{\extrarowheight}{5pt}
	\begin{longtable}{p{0.6in}|p{5.5in}}
	  2019 & \bibentry{chodrow2019multigraphs} \\
	  	   & \bibentry{Chodrow2019} \\ 
	  	   % & \bibentry{Schwarze2019} \\ 
	  	   & \bibentry{Chodrow2018} \\ 
	  % 2018 & \bibentry{Strano2018} \\ 
	  2017 & \bibentry{Chodrow2017a} \\
	  	   & \bibentry{Chodrow2017} \\ 
\hide{
	  % 2016 & \bibentry{chodrow2016demand}  \\ 
	  2013 & \bibentry{chodrow2013upper}}
	\end{longtable}

\section*{Recognitions, Honors, and Grants}
	\vspace{-10pt}
	\setlength{\extrarowheight}{5pt}
	\begin{longtable}{p{0.6in}|p{5.5in}}
		2017-20 & {\bf NSF Graduate Research Fellowship} supporting research into mathematical modeling of social and urban systems. \\ 
		2018 & {\bf Goodwin Award Nominee} by MIT Operations Research Center for ``conspicuously effective teaching.'' \\ 
		2012 & {\bf Fulbright Scholarship} supporting a year of research in Oslo, Norway. \\
			 & {\bf Ivy Award} ``recognizing the man of the graduating class who is outstanding in leadership, scholarship, and contributions to the Swarthmore College community.''\\
			 & {\bf Phi Beta Kappa} inducted member. \\
		\hide{
			& {\bf Brinkmann Award} recognizing ``the best student paper on a mathematical subject.'' \\
			2010 & {\bf Eugene Lang Summer Initiative Grant}, supporting undergraduate research. \\}
	\end{longtable}


\section*{Invited Talks}
	\vspace{-10pt}
	\begin{longtable}{p{0.6in}|p{5.5in}}
	2020 & \textbf{Local Techniques in Adaptive Voter Models.} AMS Eastern Sectional Meeting, Tufts University, Medford MA \\
	2019 & \textbf{Features, Space, and Feature Space: Learning the Structure of Segregation.} Conference on Complex Systems, Singapore \\ 
	& \textbf{Divergence, Entropy, Information: An Opinionated Introduction to Information Theory.} Society of Young Network Scientists, Burlington, VT \\ 
	& \textbf{Configuration Models of Random Hypergraphs.} Network Science Institute, Northeastern University, Boston MA \\ 
	2018 & \textbf{What's the Fuss about Power Laws?} ORC Student Seminar, MIT, Cambridge, MA. \\ 
	2017 & \textbf{The Structure of Spatial Segregation.} Growth Lab Seminar, Harvard Kennedy School, Cambridge, MA. 
	\end{longtable}


\section*{Selected Contributed Talks}
	\vspace{-10pt}
	\begin{longtable}{p{0.6in}|p{5.5in}}
	2019 & \textbf{Moments of Uniformly Random Multigraphs with Fixed Degree Sequences} \\ 
		&\quad Northeastern University, Boston, MA 2019 \\ 
		& \textbf{Configuration Models of Random Hypergraphs and their Applications} \\
		&\quad Conference on Network Science, Burlington, VT, 2019 \\ 
		&\quad SIAM Workshop on Network Science, Snowbird, UT, 2019 \\ 
	2018-19 & \textbf{Equilibrium Community Structure in Binary-State Adaptive Voter Models.} \\ 
		&\quad Conference on Complex Systems, Singapore, 2019 \\
		&\quad SIAM Workshop on Network Science, Portland, OR, 2018 \\
		&\quad International Conference on Complex Systems, Cambridge, MA, 2018  \\
		&\quad Conference on Complex Networks, Northeastern University, Boston, MA 2018 \\
	2016-20 & \textbf{Information-Geometry of Spatial Segregation} \\
		&\quad Conference on Network Science, Indianapolis, IN, 2017 \\
		&\quad Conference on Complex Systems, Amsterdam, The Netherlands, 2016 \\
	2016 & \textbf{Demand and Congestion in Multiplex Transportation Networks.} \\ 
	&\quad Conference on Complex Systems, Amsterdam, The Netherlands, 2016
	\end{longtable}

\section*{Selected Teaching}
	\vspace{-10pt}
	\begin{longtable}{p{0.6in}|p{5.5in}}
	   
	  2017-   & \textbf{Curriculum-Designer and Instructor}: \\ 
	          & \quad Computing in Optimization and Statistics (PhD level), MIT \\ 
	  		  & \quad  Statistical Programming for Business Analytics (masters level), MIT  \\
	  2018	& \textbf{Head Teaching Assistant} \\
	  		&\quad 6.268, Network Science and Models (masters and PhD level), MIT \\ 
	  2017	& \textbf{Teaching Assistant} \\ 
	  		&\quad 6.431, Introduction to Probability, MIT (undergraduate and masters level) \\ 
	  		&\quad       1.208, Human Mobility and Networks, MIT (masters level) \\ 
	  \hide{2016 & \textbf{Group Co-Leader}: Workshop in Predictive Policing, ICERM, Providence, RI.  \\}
	  \hide{
	  	2012 & \textbf{Teaching Assistant} "The Philosophy of Action", Universitet i Oslo, Norway \\
		2009-12 & \textbf{Mathematics Academic Support}, Swarthmore College, Swarthmore PA. \\
			    & \textbf{Writing Associate and Thesis Mentor}, Swarthmore College, Swarthmore PA.\\
  		% 2012 & \textbf{Teaching Assistant} for intermediate-level course on the philosopy of Plato with Professor Grace Ledbetter at Swarthmore College, Swarthmore PA. 
	  }
	\end{longtable}

\section*{Software}
	\vspace{-10pt}
	\subsection*{Educational}
	\vspace{-10pt}
	\begin{longtable}{p{0.6in}|p{5.5in}}
		  2019- & \textbf{Statistical Programming for Business Analytics} (masters level)  \\
		  	   &\quad \url{https://philchodrow.github.io/mban_orientation/} \\ 
		  2017-	   &  \textbf{Computing in Optimization and Statistics} (PhD level)\\ 
		  	   & \quad 2017: \url{https://philchodrow.github.io/cos_2017/} \\ 
		  	   & \quad 2018: \url{https://philchodrow.github.io/cos_2018/} 
		\end{longtable}

	\subsection*{Research}
	\vspace{-10pt}
	\begin{longtable}{p{0.6in}|p{5.5in}}
		  2019 & \textbf{Configuration Models of Random Hypergraphs}  \\
		  	   &\quad \url{https://github.com/PhilChodrow/hypergraph} \\ 
		  	   &  \textbf{Moments of Uniformly Random Multigraphs} \\ 
		  	   & \quad \url{https://github.com/PhilChodrow/multigraph_moments} \\ 
		  2017 & \texttt{compx}: \textbf{Learning the structure of segregation} \\ 
		  	   & \quad \url{https://github.com/PhilChodrow/compx} 
		\end{longtable}


\pagebreak
\hide{
	\section*{Academic Service}
		\vspace{-10pt}
		\begin{longtable}{p{0.6in}|p{5.5in}}
		  2018 & \textbf{Organizer:} Seminar on Operations Research for Social Good, MIT\\ 
		  2016- & \textbf{Reviewer}. \emph{Chaos}; \emph{PLoS ONE}; \emph{International Journal of Geographic Information Systems}; \emph{Computers, Environment, and Urban Systems}  \\
		  2016- & \textbf{Program Committee Member}. NetSci-X, Conference on Complex Systems, International Conference on Complex Systems 
		\end{longtable}
	}



\hide{
	\section*{Other  Experience}
		\vspace{-10pt}
		\begin{longtable}{p{0.6in}|p{5.5in}}
		  2018  & \textbf{Summer School} in Economic Networks, Oxford, UK \\ 
		  2013-15 & \textbf{Analyst}, Health Leads, Boston MA \\
		  2012-14 & \textbf{Research Assistant}, Laboratory for Quantitative Medicine, Cambridge MA \\ 
		  2012-13 & \textbf{Visiting Researcher}, Center for the Study of Mind in Nature, Oslo, Norway \\
		  % 2011-12 & \textbf{Senior Honors Thesis} in philosophy, entitled \emph{Perception and Moral Goodness}, Swarthmore College. \\
		  2010    & \textbf{REU Fellow} in matrix analysis, College of William and Mary, Williamsburg VA \\
		  2009    & \textbf{Research Assistant} in theoretical plasma physics, James Madison University, Harrisonburg VA  
		\end{longtable}
}


% \hide{
	\section*{Community Service}
		\vspace{-10pt}
		\begin{longtable}{p{0.6in}|p{5.5in}}
		  2017- & \textbf{Instructor}, Harvard Aikikai, Cambridge MA \\ 
		  & \textbf{Board Member}, Aikido Tekkojuku of Boston, Somerville MA \\ 
		  \hide{2015-16 & \textbf{Analytics Consultant}, Health Leads, Boston MA \\}
		  2010-12   & \textbf{Cofounder and Director}, NinjaGram Charities, Swarthmore College, Swarthmore PA\\
		  \hide{2011-12 & \textbf{Assistant Children's Instructor}, Aikido Kokikai of Swarthmore, Swarthmore PA\\}
		  \hide{2008-12 & \textbf{Cofounder and Director}, Swarthmore Martial Arts Club, Swarthmore PA}
		\end{longtable}
% }
\section*{Other}
	
	\textbf{Languages}: English (native), German (reading and listening), Norwegian Bokmal (reading)

	\textbf{Software}: \texttt{R}, Python,  \LaTeX, Linux

	\textbf{Activities}: Aikido: \emph{1st dan (Aikikai).} Chess: \emph{Virginia State High School Champion (2008)}

% Footer
\hide{\bigskip
\begin{center}
  \begin{footnotesize}
    Last updated: \today
  \end{footnotesize}
\end{center}}

\nobibliography{pubs}
\end{document}