%!TEX root = ../cv.tex
%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Teaching}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------

  \cventry
      {Instructor of Record}
      {Python Programming with Applications II}
      {UCLA Dept. of Mathematics}
      {2021-}
      {A project-based course in advanced computational science using the Python programming language, including linear algebra and optimization, network science, machine learning, and data visualization.
      Original syllabus and design.}

  \cventry
    {Instructor of Record}
    {PIC16A: Python Programming with Applications I}
    {UCLA Dept. of Mathematics}
    {2020-}
    {A flipped and project-based introduction to Python programming, with an emphasis on scientific computing, data analysis, and machine learning. Delivered remotely due to the COVID19 pandemic.
    Original syllabus and design.}

  \cventry
    {Organizer and Instructor} % Degree
    {Computing in Optimization and Statistics} % Institution
    {MIT ORC} % Location
    {2015 - 2020} % Date(s)
    {A graduate student-led seminar in principles and tools for computational data science and analytics.} % description

  \cventry
    {Organizer and Instructor} % Degree
    {Software Tools for Data Science} % Institution
    {MIT ORC} % Location
    {2017-2020} % Date(s)
    {A sequence in computational tools for data science, offered to new students in the Masters of Business Analytics program at MIT. Original syllabus and design.}  
  
  \cventry
    {Head Teaching Assistant} % Degree
    {6.268, Network Science and Models} % Institution
    {MIT Dept. of EECS} % Location
    {2018} % Date(s)
    {Responsibilities including exam-writing, grading, management of TAs, active-learning tutorial sections, project mentorship, and project evaluations.}  

\cventry
    {Teaching Assistant} % Degree
    {6.431, Introduction to Probability} % Institution
    {MIT Dept. of EECS} % Location
    {2017} % Date(s)
    {Responsibilities including active-learning tutorial sections, office hours, and exam grading.}  
    
% \cventry
%     {Teaching Assistant} % Degree
%     {1.208, Human Mobility and Networks} % Institution
%     {MIT} % Location
%     {2017} % Date(s)
%     {}  

%---------------------------------------------------------
\end{cventries}
